\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Shrikrishna Yeole} % Your name

% Contact Information
\address{+91 7972781300 \\ Pune, Maharashtra} 
\address{%
  \href{mailto:shriyeole5002@gmail.com}{shriyeole5002@gmail.com} \\
  \href{https://www.linkedin.com/in/shrikrishna-yeole}{linkedin.com/in/shrikrishna-yeole} \\
  \href{https://github.com/Shri5001}{github.com/shri5001}
}

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------
\begin{rSection}{OBJECTIVE}
Computer Engineering graduate (2024) with hands-on training in AWS, Linux, and DevOps tools. Seeking an entry-level AWS/DevOps Engineer role to apply knowledge of EC2, S3, IAM, Docker, Jenkins, Git, and Terraform in building automated, secure, and scalable cloud solutions. Eager to contribute to cloud-based infrastructure and CI/CD pipeline development in a dynamic IT environment.
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}
{\bf Bachelors of Engineering, Computer Engineering (CGPA: 8.07 )} \hfill {2024}\\
SND College of Engineering and Research Center, Yeola 

{\bf HSC (62.62 )} \hfill {2020}\\
SSGM College, Kopargaon 

{\bf SSC (91.80)} \hfill {2018}\\
KBP Vidyalaya, Kopargaon 
\end{rSection}

%----------------------------------------------------------------------------------------
% TECHNICAL SKILLS	
%----------------------------------------------------------------------------------------
\begin{rSection}{TECHNICAL SKILLS}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming & Python, SQL, HTML, CSS, Java (Basic) \\
AWS Services & EC2, VPC, S3, RDS, Route53, IAM, SNS, EFS, EBS, Lambda, DynamoDB, CloudWatch. \\
DevOps Tools & Git, Terraform, Jenkins, Docker, Kubernetes, Nexus, Prometheus,Grafana, Maven, Tomcat. \\
OS & Linux, Windows
\end{tabular}\\
\end{rSection}

%----------------------------------------------------------------------------------------
% EXPERIENCE
%----------------------------------------------------------------------------------------
\begin{rSection}{EXPERIENCE}
\textbf{Cloud Computing Intern} \hfill Dec 2024 -- May 2025 \\
Paarsh Infotech Pvt. Ltd. 
\begin{itemize}
    \itemsep -3pt {}
    \item Gained hands-on experience with core AWS services: EC2, S3, IAM, Lambda, and CloudWatch.
    \item Monitored system performance and logs using AWS CloudWatch and set up alerts for key metrics.
    \item Managed version control and collaboration with Git and GitHub in team environments.
    \item Deployed applications using CI/CD pipelines with GitHub Actions, Jenkins, or AWS CodePipeline.
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------
\begin{rSection}{PROJECTS}
\textbf{Automated Java Application Deployment using Jenkins, SonarQube, Ansible, Nexus, and S3.}  
\begin{itemize}
    \item Developed a CI/CD pipeline using Jenkins to automate build, test, and deployment processes for Java applications on Tomcat servers.
    \item Integrated SonarQube for code quality analysis, Nexus for artifact storage, and S3 for cloud storage in the Jenkins pipeline.
    \item Created and executed Ansible playbooks to configure Tomcat servers and deploy WAR files across multiple production nodes.
    \item Managed artifact storage and versioning using Nexus, and automated deployment to Tomcat servers via Ansible.
\end{itemize}
\end{rSection}
%----------------------------------------------------------------------------------------
% CERTIFICATIONS
%----------------------------------------------------------------------------------------
\begin{rSection}{CERTIFICATIONS}
\begin{itemize}
    \item \textbf{AWS Cloud Practitioner Essentials} -- AWS SkillBuilder
    \item \textbf{Modern DevOps with AWS} -- Naresh IT 
    \item \textbf{Google Cybersecurity Professional Certificate} -- Coursera
\end{itemize}
\end{rSection}
\end{document}
